Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 problem_setting.tex
going through edits from david

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.

@@

\begin{assumption}[Not too many near-ties] \label{A1}
Near-ties have vanishing probability; 
that is, there exist constants
\dkedit{$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
such that 
$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.}
\end{assumption}

\dkedit{
The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
is not restrictive.
Because \TieDensity and \TieCutoff are both constants,
we could simply increase \TieDensity.
Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
while \TieCutoff is a constant,
so an alternative is to decrease \MinProb by a suitable constant factor.

Assumption~\ref{A1} implies that ties happen with probability $0$.
One special case of interest we discuss below is
$\TieDensity = 0$. This case arises when there is a cutoff
\TieCutoff such that only a measure-zero set of agents has two best arms
within utility \TieCutoff of each other.
In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
i.e., supported on a finite set of types.}

\paragraph{Roles of parameters:}
Our problem setting is characterized by many parameters.
Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
the key parameters, while we consider
$\sigma, \Diam, d, \TieDensity, \TieCutoff$ to be constant.
We track all parameters through most of our proofs,
but report final results in terms of only the three key parameters,
except where we illustrate a specific point.
\dkedit{In particular, we consider $d$ a constant, because users
typically evaluate products (or restaurants) by a small number of
relevant features.}

>>>>

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}

@@

\begin{assumption}[Not too many near-ties] \label{A1}
Near-ties have vanishing probability; 
that is, there exist constants
$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
such that 
$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
\end{assumption}

The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
is not restrictive.
Because \TieDensity and \TieCutoff are both constants,
we could simply increase \TieDensity.
Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
while \TieCutoff is a constant,
so an alternative is to decrease \MinProb by a suitable constant factor.

Assumption~\ref{A1} implies that ties happen with probability $0$.
One special case of interest we discuss below is
$\TieDensity = 0$. This case arises when there is a cutoff
\TieCutoff such that only a measure-zero set of agents has two best arms
within utility \TieCutoff of each other.
In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
i.e., supported on a finite set of types,
\pfedit{and each type has a unique best arm.}

\paragraph{Roles of parameters:}
Our problem setting is characterized by many parameters.
Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
the key parameters, while we consider
$\sigma, \Diam, d, \TieDensity, \TieCutoff$ to be constant.
We track all parameters through most of our proofs,
but report final results in terms of only the three key parameters,
except where we illustrate a specific point.
\pfcomment{We report Thm 1 with $L$ in it.  Maybe we can still leave this sentence like it is.  I'll revisit later, if someone else doesn't resolve this first.}
In particular, we consider $d$ a constant, because users
typically evaluate products (or restaurants) by a small number of
relevant features.
